---
title: "q2"
output: html_document
---

What is the yearly growth rate of Land Values over the years covered by this data? Take a simplistic model: the value is given by P=P0ertP=P0ert, where tt is measured in years. (A more complete model would give each property its own base price P(i)0P0(i).) Estimate rrover all assessments with a non-zero land value. (Hint: Consider using linear regression and logarithms.)

```{r}
data <- read.csv("Historic_Secured_Property_Tax_Rolls.csv")

library(broom)

valueyears <- data[,c("block_and_lot_number", "closed_roll_assessed_land_value", "closed_roll_fiscal_year")] %>% filter(closed_roll_assessed_land_value != 0) %>% group_by(block_and_lot_number, closed_roll_fiscal_year) %>% summarize("land_value" = closed_roll_assessed_land_value)  %>% ungroup %>% 
  spread(closed_roll_fiscal_year, land_value) 

fit <- valueyears %>% do(augment(lm(`2007`~`2008` | `2014`, data=.), data=.))

select(fit, .fitted) %>% arrange() %>% tbl_df
```

We can use the property locations to estimate the areas of the neighborhoods. Represent each as an ellipse with semi-axes given by a single standard deviation of the longitude and latitude. What is the area, in square kilometers, of the largest neighborhood measured in this manner? Be sure to filter out invalid coordinates.

```{r, echo=FALSE}
library(stringr)
library(tidyr)

datawarea <- filter(data, Location != "") %>% separate(Location, into = c("lat", "long"), sep = ",")
  
datawarea$lat <- str_replace(datawarea$lat, "\\(", '')
datawarea$long <- str_replace(datawarea$long, "\\)", '')

neighborhood_areas <- group_by(datawarea, Neighborhood.Code) %>% summarize(sd_lat = sd(lat)*110.57, sd_long = sd(long)*111.32 )

neighborhood_areas <- mutate(neighborhood_areas, axes = sqrt(sd_lat*sd_lat + sd_long*sd_long)) %>% mutate(area = (axes*axes*pi))

largest <- sort(neighborhood_areas$area, decreasing = TRUE)[2]
7.689157 
```

